### 2018-01-26 ApproxComp/sec-data.tex

Link prediction methods are often applied to very large and sparse networks, which has a large {\em search space} $O(n^2)$,
where $n$ is the number of nodes. Hence, the scalability is a big challenge. In fact, an often overlooked fact is that most {\em exiting link prediction algorithms evaluate the link propensities only over a subset of possibilities rather than all propensities over the entire network},
\eg \cite{zhu2016}..
In order to understand why this is the case, consider a large network with $10^8$ nodes. Its number of {\em possibilities} for links
is of the order of $10^{16}$. Therefore, a 3GHz processor would
require at least $35$ days just to allocate one {\em machine cycle} to
every pair of nodes. This implies that in order to determine the
top-ranked link predictions over the {\em entire network}, the
running time will be much much larger than $35$ days.

@@

Latent factor models have been shown to be wildly successful in the domain of
collaborative filtering, but not link prediction in spite of the obvious
similarity between link prediction and collaborative filtering and
the obvious effectiveness of latent factor models. One of the reasons why latent factor models are rarely used for
link prediction is due to their complexity. In
collaborative filtering applications, the item dimension is of the
order of a few hundred thousand, whereas even the smallest  real-world networks contain more than a million nodes.
Even worse, we also experientially find that the quality of link prediction for latent factor models decreases with the increase of data sparsity,
and networks typically become sparser when their sizes grow larger.

@@

We experimentally show that our ensemble approach is over $50$ times faster and  over $20\%$ more accurate than {\sc bigclam} \cite{yang-wsdm2013} on using real-life social networks.

>>>>

Link prediction methods are often applied to very large and sparse networks, which have a large {\em search space} $O(n^2)$,
where $n$ is the number of nodes. Hence, the scalability is a big challenge. In fact, an often overlooked fact is that most {\em exiting link prediction algorithms evaluate the link propensities only over a subset of possibilities rather than all propensities over the entire network},
\eg \cite{zhu2016}.
In order to understand why this is the case, consider a large network with $10^8$ nodes. Its number of {\em possibilities} for links
is of the order of $10^{16}$. Therefore, a 3GHz processor would
require at least $35$ days just to allocate one {\em machine cycle} to
every pair of nodes. This implies that in order to determine the
top-ranked link predictions over the {\em entire network}, the
running time will be much much larger than $35$ days.

@@

Latent factor models have proven a great success in the domain of
collaborative filtering, but not link prediction in spite of the obvious
similarity between link prediction and collaborative filtering and
the obvious effectiveness of latent factor models. One of the reasons why latent factor models are rarely used for
link prediction is due to their complexity. In
collaborative filtering applications, the item dimension is of the
order of a few hundred thousand, whereas even the smallest  real-world networks contain more than a million nodes.
Even worse, we also experientially find that the quality of link prediction for latent factor models decreases with the increase of data sparsity,
and networks typically become sparser when their sizes grow larger.

@@

We experimentally show that our ensemble approach is over $50$ times faster and  over $20\%$ more accurate than {\sc bigclam} \cite{yang-wsdm2013} using real-life social networks.
